Testing Charts: viewers' perceptual accuracy in surveys

### 2023-07-24 SDSS-2023/testing-charts-accuracy.qmd
household income

@@

income <- round_123 %>% 
  ggplot(aes(x = income4)) + 
  geom_bar(aes(weight = weight_pct_round), fill="grey", colour = "grey30", linewidth=0.5) + 
  ylab("Percent") + 
  ggtitle("Income levels") +
  theme(axis.text.x = element_text(angle=30, hjust = 1)) +
  xlab("") + ylim(c(0,40)) +
  facet_grid(.~chart) +
  geom_segment(
    aes(
      x = as.numeric(income) - 0.45,
      y = value,
      xend = as.numeric(income) + 0.45,
      yend = value,
      linetype=group
    ), 
    alpha = 1, colour = "black", linewidth = 0.25,
    data = omni_income
  )  +
  scale_linetype_manual(values=c(2,2,1)) +
  theme(legend.position = "none")

>>>>

acs_income <- data.frame(
  income4 = c("< $30k", "$30k - $60k", 
              "$60k - $100k", "more than $100k"), 
  percent = c(6+3.9+7.5+ .5*7.8, 
              .5*7.8 + 11.3 + .4*16.8, 
              .6*16.8+12.8,
              16.3+7.9+9.8))

# Household income
#     Less than $10,000	6.0
#     $10,000 to $14,999	3.9
#     $15,000 to $24,999	7.5
#     $25,000 to $34,999	7.8
#     $35,000 to $49,999	11.3
#     $50,000 to $74,999	16.8
#     $75,000 to $99,999	12.8
#     $100,000 to $149,999	16.3
#     $150,000 to $199,999	7.9
#     $200,000 or more	9.8

# 
# acs_income <- data.frame(
#   income4 = c("< $30k", "$30k - $60k", 
#               "$60k - $100k", "more than $100k"), 
#   percent = c(1807928 + 2669815 + 10192511 + .5*16440260, 
#               .5*16440260+ 21573641+ 2/3*17579780, 
#               1/3*17579780 + 8347923+13881892, 
#               21161141)/113654891*100 )
# Population age 18 and over
# FULL-TIME, YEAR-ROUND WORKERS WITH EARNINGS	113654891	79395	
#     $1 to $9,999 or loss	1807928	11027	1.6	0.1
#     $10,000 to $14,999	2669815	16330	2.3	0.1
#     $15,000 to $24,999	10192511	50628	9.0	0.1
#     $25,000 to $34,999	16440260	63750	14.5	0.1
#     $35,000 to $49,999	21573641	44746	19.0	0.1
#     $50,000 to $64,999	17579780	35183	15.5	0.1
#     $65,000 to $74,999	8347923	32204	7.3	0.1
#     $75,000 to $99,999	13881892	50191	12.2	0.1
#     $100,000 or more	21161141	100258	18.6	0.1

@@

income <- round_123 %>% 
  ggplot(aes(x = income4)) + 
  geom_bar(aes(weight = weight_pct_round), fill="grey", colour = "grey30", linewidth=0.5) + 
  ylab("Percent") + 
  ggtitle("Income levels (Family)") +
  theme(axis.text.x = element_text(angle=30, hjust = 1)) +
  xlab("") + ylim(c(0,40)) +
  facet_grid(.~chart) +
  geom_point(aes(y = percent), data = acs_income) +
  geom_segment(
    aes(
      x = as.numeric(income) - 0.45,
      y = value,
      xend = as.numeric(income) + 0.45,
      yend = value,
      linetype=group
    ), 
    alpha = 1, colour = "black", linewidth = 0.25,
    data = omni_income
  )  +
  scale_linetype_manual(values=c(2,2,1)) +
  theme(legend.position = "none")
